---
title: "432 Assignment 1"
author: "Corbin"
date: "2023-01-11"
output: html_document
---

[My GitHub](https://github.com/CBMontminy/BIOL432_Assignment1)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Adding packages and theme
```{r, include=F}
library(dplyr)
library(ggplot2)
source("http://bit.ly/theme_pub")
```


# Running script that generates original data
```{r, include=F}
source("dataGenerato.R")
```

# Running script that adds volume data and rewrites csv.
```{r, include=F}
source("volumeEstimato.R")
```

Loading measurement data
```{r}
read.csv("measurements.csv")
```
$ Arranging data by organism, observer, and volume
```{r}
Orgnsm=arrange(MyData, Organism)
print(Orgnsm)
Obs=arrange(MyData, Observer)
print(Obs)
Vol=arrange(MyData, Volume)
print(Vol)
```

# Creating Subsets for each species type
```{r}
Silvestris=subset(MyData, Organism=="Felis silvestris")
Leo=subset(MyData, Organism=="Panthera leo")
Pardus=subset(MyData, Organism=="Panthera pardus")
Tigris=subset(MyData, Organism=="Panthera tigris")
Concolor= subset(MyData, Organism=="Puma concolor")
```

# Calculating average volume for each species and creating an average volume data frame
```{r}
Average_Volume=c(mean(Silvestris$Volume), mean(Leo$Volume), 
                 mean(Pardus$Volume), mean(Tigris$Volume), mean(Concolor$Volume))

Species=c("Felis silvestris", "Panthera leo", 
          "Panthera pardus", "Panthera tigris", "Puma concolor")


AvgVol=data.frame(Species,Average_Volume)
print(AvgVol)


Observations= MyData %>% 
  group_by(Organism, Observer) %>% count(Organism)
print(Observations)
```

# Creating volume distribution boxplot
```{r}
Figure1=ggplot(MyData, aes(x=Organism, y=Volume, color=Organism)) + 
  labs(x="Species", y="Limb Volume", 
       caption="Figure 1: Limb volume distribution by species. The red data represents the species Felis silvestris.  The \nyellow data represents the species Panthera leo.  The green data represents the species Panthera pardus.  \nThe blue data represents the species Panthera tigris.  The purple data represents the species Puma concolor.") +
  geom_boxplot() + theme_pub()+
  theme(plot.caption= element_text(hjust=0))
print(Figure1)
```

# Creating frequency histogram
```{r}
Hist=ggplot(MyData, aes(x=Volume, fill=Organism)) +
  geom_histogram(bins=8)+
  facet_grid(cols=vars(Organism))+
  labs(x="Limb Volume",y="Count",
       caption="Figure 2: Limb volume frequency histigram by secies.  The red data represents the species Felis silvestris.  The \nyellow data represents the species Panthera leo.  The green data represents the species Panthera pardus.  The \nblue data represents the species Panthera tigris.  The purple data represents the species Puma concolor.")+
  theme(plot.caption= element_text(hjust=0))
print(Hist)
```

